Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-11 cmsb22.tex
Come back to the original option

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns \(n\) and \(s\) denote the numbers of nodes (resp.\ input nodes) of each model. For each method, Column \(|M|\) denotes the number of minimal trap spaces and the computation time is given in seconds.
    ``DNF'' means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_original_option}
  \begin{tabular}{lrrrrrr}
    \toprule
    & & & \multicolumn{2}{c}{PyBoolNet} & \multicolumn{2}{c}{Trappist} \\
    \cmidrule(lr){4-5} \cmidrule(lr){6-7}
    model & \(n\) & \(s\) & \(|M|\) & time (s) & \(|M|\) & time (s) \\
    \midrule
    inflammatory-bowel-disease & 47 & 0 & 0+ & DNF & 1 & 21.90 \\
    T-LGL-survival-network-2008 & 61 & 7 & 318 & 0.73 & 318 & 0.14 \\
    SN-5 & 2746 & 829 & 0+ & DNF & 0+ & DNF \\
    \bottomrule
  \end{tabular}
\end{table}

\vangiang{Original option: We set a limit of 1000 for the number of minimal trap spaces and a limit of 2 minutes for the computation time. There will be 4 cases (see Table~\ref{tab:selected_original_option}). Case 1: both methods finished (e.g., the T-LGL-survival-network-2008 model). In this case, we simply compare the computation time between two methods. Case 2: PyBoolNet finished and Trappist did not finish. In this case, PyBoolNet is of course better than Trappist (but no model for this case). Case 3: PyBoolNet did not finish and Trappist finished (e.g., the inflammatory-bowel-disease). In this case, Trappist is of course better than PyBoolNet. Moreover, 0+ indicates that PyBoolNet even failed at the computation of prime-implicants. Case 4: both methods did not finish. In this case, we consider the following subcases. Case 4-1: PyBoolNet is 0+ and Trappist is 0+ (e.g., the SN-5 model), i.e., PyBoolNet failed at the computation of prime-implicants and Trappist failed at the conversion to PNML models. Case 4-2: PyBoolNet is 0+ and Trappist is 1000+ (no model for this case), i.e., Trappist is better than PyBoolNet. Case 4-3: PyBoolNet is 1000+ and Trappist is 0+ (no model for this subcase), i.e., PyBoolNet is better than Trappist. Case 4-4: PyBoolNet is 1000+ and Trappist is 1000+ (no model for this case), i.e., we cannot compare between PyBoolNet and Trappist.}
